---
title: 'Milestone project'
output: 
  #pdf_document: default
  html_document:
    keep_md: yes
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```
Importing the required libraries
```{r}
library(stringi)
library(kableExtra)
library(dplyr)
library(ngram)
library(plotly)
```
Importing the data
```{r}
blogs <- readLines("./final/en_US/en_US.blogs.txt")
news <- readLines("./final/en_US/en_US.news.txt", skipNul = T, warn = F)
twitter <- readLines("./final/en_US/en_US.twitter.txt", skipNul = T, warn = F)
```
Showing some general information about the files
```{r}
gen_stats <- data.frame(Size = sapply(list(blogs, news, twitter), function(x) {format(object.size(x), "MB")}),
                                    t(rbind(sapply(list(blogs, news, twitter), stri_stats_general))), 
                                    t(rbind(sapply(list(blogs, news, twitter), stri_stats_latex))))

rownames(gen_stats) <- c("Blogs", "News", "Twitter")

kable(gen_stats, 'html') %>% kable_styling(full_width = F)
```
Getting a sample from the data
```{r}
set.seed(123456)
n <- 1000
blog_sample <- sample(blogs, n)
news_sample <- sample(news, n)
twitter_sample <- sample(twitter, n)
sample_data <- c(blog_sample, news_sample, twitter_sample)
```
Showing some general information about the sample
```{r}
sample_stats <- data.frame(Size = sapply(list(blog_sample, news_sample, twitter_sample, sample_data), function(x) {format(object.size(x), "MB")}),
                            t(rbind(sapply(list(blog_sample, news_sample, twitter_sample, sample_data), stri_stats_general))), 
                            t(rbind(sapply(list(blog_sample, news_sample, twitter_sample, sample_data), stri_stats_latex))))
rownames(sample_stats) <- c("blog_sample", "news_sample", "twitter_sample", "sample_data")

kable(sample_stats, 'html') %>% kable_styling(full_width = F)
```
Removing all the punctuation marks
```{r}
sample_data <- lapply(sample_data, preprocess, remove.punct = T)
sample_data <- paste(sample_data, collapse = "")
```
Getting the first 4 n-grams for the sample
```{r}
unigram <- ngram(sample_data, n = 1) %>% get.phrasetable
bigrams <- ngram(sample_data, n = 2) %>% get.phrasetable
trigram <- ngram(sample_data, n = 3) %>% get.phrasetable
fourgram <- ngram(sample_data, n = 4) %>% get.phrasetable
```
Plotting bar charts for the first 4 n-grams
```{r}
plot_ly(unigram[1:20,], x = ~ngrams, y = ~freq, color = I("dodgerblue3")) %>%
  layout(xaxis = list(categoryorder = "total descending"))
```
```{r}
plot_ly(bigrams[1:20,], x = ~ngrams, y = ~freq, color = I("darkgoldenrod2")) %>%
  layout(xaxis = list(categoryorder = "total descending"))
```
```{r}
plot_ly(trigram[1:20,], x = ~ngrams, y = ~freq, color = I("coral2")) %>%
  layout(xaxis = list(categoryorder = "total descending"))
```
```{r}
plot_ly(fourgram[1:20,], x = ~ngrams, y = ~freq, color = I("navajowhite2")) %>%
  layout(xaxis = list(categoryorder = "total descending"))
```

## Conclusion
After visualizing the tables for the sample datas we can 
deduce that the most common n-gram has a very low frequency, this is,
even the number of times a 1-gram is written in the data is small compared to the number of words.